Who does big team science?

### 2023-03-16 manuscript_scopus.Rmd
adding all the parts

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp")

@@

We have defined **BTS publications** as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (`ani`) database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences.

@@

***Publication Metrics***. For each author, we will calculate the total
number of publications, the h-index, and the i-10 index. The h-index
represents the highest *h* number of publications that have at least *h*
citations, while the i-10 index represents the number of publications
with at least 10 citations.

@@

-   Number of articles for inclusion: total, separated by four subject
    areas, presenting graphics of the number of publication across time

total

13581

+----------------+-----+
|publication_type|count|
+----------------+-----+
|              sh|   41|
|              cp|  266|
|              ar|12689|
|              dp|    4|
|              pp|  580|
|              ip|    1|
+----------------+-----+

subject area 
+-----------------+-----+
|      SubjectArea|count|
+-----------------+-----+
|  Health Sciences|10685|
|Physical Sciences| 6151|
|Multidisciplinary| 1569|
|  Social Sciences|  543|
|    Life Sciences| 7686|
+-----------------+-----+

time

pub_time_count

@@

Out[52]: 2534

+-----------------+------------+
|      SubjectArea|count(srcid)|
+-----------------+------------+
|  Health Sciences|        1472|
|Physical Sciences|         641|
|Multidisciplinary|          14|
|  Social Sciences|         206|
|    Life Sciences|        1024|
+-----------------+------------+

-   Statistics (mean, median, standard deviation, minimum, maximum) of
    the journal impact using Source Normalized Impact per Paper for the
    four subject areas.

+-----------------+------------------+------------------+---------+------------+---------+
|      SubjectArea|         avg(snip)| stddev_samp(snip)|min(snip)|median(snip)|max(snip)|
+-----------------+------------------+------------------+---------+------------+---------+
|  Health Sciences|  4.39848449724717|7.1846479513521615|      0.0|       2.078|  173.932|
|Physical Sciences|1.7298434289762685| 1.336672368345959|    0.155|       1.278|   30.405|
|Multidisciplinary| 6.092944123314063|   4.3151334953509|    0.032|       3.341|   11.342|
|  Social Sciences| 2.204784860557769|2.1441319264666743|    0.017|       1.605|   30.405|
|    Life Sciences| 2.524247249015079| 2.044898988084329|    0.017|       1.742|   12.624|
+-----------------+------------------+------------------+---------+------------+---------+

@@

pub_time_subject

@@

keywords

@@

+-----------+
|count(auid)|
+-----------+
|     257536|
+-----------+

@@

	count(Authorseq)	avg(Authorseq)	stddev_samp(Authorseq)	min(Authorseq)	median(Authorseq)	max(Authorseq)
0	13581	49.904646	207.006114	10	19.0	5155

@@

author_time

We will use $\alpha$ \< .05 for all analyses that involve hypothesis
testing. We make no directional predictions.

@@

career_time

-   To analyze trends over time, we will calculate the average career
    length for each publication (i.e., average the author career length
    to create one score for each paper) and run a regression analysis
    using career length to predict year of publication. A positive slope
    for year of publication would indicate increasing years of first
    publication (i.e., more younger scholars over time), while a
    negative slope would indicate older years of first publication
    (i.e., more older scholars over time).
-   In order to show variance between individuals, we calculate the
    standard deviation of career length for each publication and run a
    regression analysis using this variance representation to predict
    publication year. A positive slope would indicate increasing
    variance over time (i.e., more diversity in the career lengths of
    scholars), while a negative slope would indicate less variance and
    diversity in scholars over time.
-   These analyses will be completed separately for each of the four
    large subject areas.

------ Physical Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.531373   0.030990  -17.146   0.000000
##  -0.207000   0.059698   -3.467   0.000533
## 2020.342936   0.367600 5496.040   0.000000
## ---
## Mean squared error:  30.862113 , RMSE:  5.555368
## Multiple R-squared: 0.145118 ,             Total iterations: 0
------------

------ Social Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.437422   0.093563   -4.675   0.000004
##  -0.104549   0.146459   -0.714   0.475750
## 2019.182625   0.764850 2639.973   0.000000
## ---
## Mean squared error:  30.685713 , RMSE:  5.539469
## Multiple R-squared: 0.118772 ,             Total iterations: 0
------------

------ Health Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.460876   0.019674  -23.425   0.000000
##  -0.218675   0.037611   -5.814   0.000000
## 2019.076458   0.231406 8725.260   0.000000
## ---
## Mean squared error:  30.039405 , RMSE:  5.480822
## Multiple R-squared: 0.144584 ,             Total iterations: 0
------------

------ Life Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.604957   0.026519  -22.812   0.000000
##  -0.056843   0.046915   -1.212   0.225716
## 2019.490201   0.276602 7301.067   0.000000
## ---
## Mean squared error:  27.654316 , RMSE:  5.258737
## Multiple R-squared: 0.175747 ,             Total iterations: 0
------------

@@

+----------------------+
|count(affiliation_ids)|
+----------------------+
|                 35114|
+----------------------+

inst time

@@

pub_type versus normal_pub_type

@@

    We will report descriptive statistics on the total number of publications and h-index for individuals overall.
        Do this for each unique person and report averages
        Do this for each publication and create an average for each publication
    Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
    A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
    We will separate these by each of the four subject areas.

	avg_pub_count	std_pub_count
0	4.451816	6.901369

	avg(avg_pub_count AS mean_of_avg_pub_count)	stddev_samp(avg_pub_count AS std_of_avg_pub_count)	avg(std_pub_count AS mean_of_std_pub_count)	stddev_samp(std_pub_count AS std_of_std_pub_count)
0	7.581413	5.797233	7.140015	5.10383

	avg_HIndex	std_HIndex	med_HIndex
0	14.242142	43.798203	2.0

	avg_of_avg_HIndex	std_of_avg_HIndex	avg_of_std_HIndex	std_of_std_HIndex	med_of_med_HIndex
0	28.136255	38.013819	36.430509	46.474619	5.0

------ Physical Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.004420   0.022715   -0.195   0.845717
##  -0.105746   0.034058   -3.105   0.001922
## 2015.347578   0.195556 10305.717   0.000000
## ---
## Mean squared error:  35.756076 , RMSE:  5.979638
## Multiple R-squared: 0.009554 ,             Total iterations: 0
------------

------ Social Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.335536   0.179536   -1.869   0.062389
##   0.130796   0.186924    0.700   0.484517
## 2016.658826   0.487148 4139.727   0.000000
## ---
## Mean squared error:  34.070868 , RMSE:  5.837026
## Multiple R-squared: 0.021558 ,             Total iterations: 0
------------

------ Health Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.235551   0.028158   -8.365   0.000000
##  -0.006692   0.026612   -0.251   0.801476
## 2014.979175   0.119976 16794.893   0.000000
## ---
## Mean squared error:  33.860172 , RMSE:  5.818949
## Multiple R-squared: 0.035782 ,             Total iterations: 0
------------

------ Life Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.430599   0.037807  -11.389   0.000000
##   0.133215   0.034255    3.889   0.000102
## 2016.008237   0.147870 13633.624   0.000000
## ---
## Mean squared error:  31.736306 , RMSE:  5.633499
## Multiple R-squared: 0.054081 ,             Total iterations: 0
------------

@@

total number of unique GP for each publication 
using year to predict GP 
positive slope means that as year goes up number of GP goes up 
negative slope means that as year goes up number of GP goes down 
forest plot of the effects + confidence interval

------ Physical Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.061001   0.022958   -2.657   0.007923
## 130.518393  46.247823    2.822   0.004802
## ---
## Mean squared error:  56.853041 , RMSE:  7.540096
## Multiple R-squared: 0.002357 ,             Total iterations: 0
------------

------ Social Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.077040   0.058153   -1.325   0.186023
## 160.766462 117.214988    1.372   0.170993
## ---
## Mean squared error:  45.807761 , RMSE:  6.768143
## Multiple R-squared: 0.004491 ,             Total iterations: 0
------------

------ Health Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.017775   0.009794   -1.815   0.069578
##  40.118948  19.718323    2.035   0.041926
## ---
## Mean squared error:  25.532574 , RMSE:  5.052977
## Multiple R-squared: 0.000434 ,             Total iterations: 0
------------

------ Life Sciences ------

Note: the last rows are the information for Intercept
## -------------------------------------------------
##   Estimate   |   Std.Error | t Values  |  P-value
##  -0.014946   0.010485   -1.425   0.154081
##  34.499812  21.117788    1.634   0.102392
## ---
## Mean squared error:  17.279398 , RMSE:  4.156850
## Multiple R-squared: 0.000434 ,             Total iterations: 0
------------

-   Last, we will examine the differences in representation for
    corresponding author sets versus all other authors. For papers with
    10 to 49 authors, we will use the three first authors and the last
    author to compare against other authors. For 50 to 99 authors, five
    first authors plus last will be used, and for all papers with more
    than 100 authors, we will use ten first authors and the last author.
    We will calculate the frequencies of each of the UN Sub-Regions for
    first authors versus other authors, converting these values to
    proportions. Given the expected small sample sizes of these
    contingency tables, we will group together titles based on the year
    of publication (assuming at least 5 publications per year, these may
    be binned by 5-year or smaller increments to increase sample size).
    For each grouping, we will calculate the effect size of the
    differences in frequencies comparing first authors to all other
    authors. Since this data is categorical, we will use Cramer's V to
    represent the effect size. If the effect size includes zero in its
    confidence interval, this result will imply that first and all other
    authors represent the same pattern of UN Sub-Region diversity. Any
    confidence interval that does include zero represents a difference
    in diversity. We will report these values and discuss what regions
    of the world are represented when effect sizes indicate a difference
    from zero using standardized residuals.

    ## fix the stupid CIs

```{r small-effects}
DF$small_first_gp <- DF$small_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r medium-effects}
DF$medium_first_gp <- DF$medium_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r large-effects}
DF$large_first_gp <- DF$large_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r final-graphs}
small_author + #theme(legend.position = "none") + 
medium_author + #theme(legend.position = "none") + 
large_author + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

ggsave("figure/author_country.png", width = 10, height = 7, 
       units = "in")

small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

>>>>

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(flextable)
library(wordcloud2)
library(htmlwidgets)
library(webshot)
library(figpatch)
```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip")

@@

We have defined **BTS publications** as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (`ani`) database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences. We filtered the database to include articles, articles in press, business articles, conference papers, data papers, preprints, and surveys using Elsevier's classification system.

@@

***Publication Metrics***. For each author, we will calculate the total
number of publications, and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.

@@

-   Number of articles for inclusion: total, separated by four subject
    areas, presenting graphics of the number of publication across time
    total

```{r}
total_num <- 13581
health_num <- 10685
physical_num <- 6151
social_num <- 543
life_num <- 7686
```

The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num` Physical Sciences articles, `r social_num` Social Sciences articles, and `r life_num` Life Sciences articles. Articles could be classified into multiple categories.

```{r}
ggplot(DF$pub_time_count %>% 
         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
  ylab("Number of Articles Per Year") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

```{r}
journals <- 2534
health_journal <- 1472
physical_journal <- 641
social_journal <- 206
life_journal <- 1024
```

The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences. The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X.

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

```{r}
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(count = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary")

health_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

saveWidget(health_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/health_cloud.png", vwidth = 600, vheight = 600)

physical_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

saveWidget(physical_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/physical_cloud.png", vwidth = 600, vheight = 600)

life_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

saveWidget(life_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/life_cloud.png", vwidth = 600, vheight = 600)

social_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

saveWidget(social_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/social_cloud.png", vwidth = 600, vheight = 600)
```

```{r}
h <- fig("figure/health_cloud.png")
p <- fig("figure/physical_cloud.png") 
l <- fig("figure/life_cloud.png") 
s <- fig("figure/social_cloud.png")

h + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
p + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
l + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
s + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

```{r}
health_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(health_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/health_key.png", vwidth = 600, vheight = 600)

physical_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count), 
             minSize = 20)

saveWidget(physical_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/physical_key.png", vwidth = 600, vheight = 600)

life_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(life_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/life_key.png", vwidth = 600, vheight = 600)

social_cloud <- wordcloud2(DF$keywords  %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(social_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/social_key.png", vwidth = 600, vheight = 600)
```

```{r}
h <- fig("figure/health_key.png")
p <- fig("figure/physical_key.png") 
l <- fig("figure/life_key.png") 
s <- fig("figure/social_key.png")

h + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
p + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
l + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
s + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

```{r}
total_authors <- 257536
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

The total number of unique authors across all publications was `r total_authors`.

@@

The mean number of authors per publication was *M* = `r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of `r min_authors` to `r max_authors`.

@@

```{r}
avg_author_time <- 
  DF$author_time %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  filter(Number_Papers >= 3) %>% 
  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))

ggplot(avg_author_time, aes(Year, Average_Num_Authors)) + 
  theme_classic() + 
  geom_point(aes(size = Number_Papers)) + 
  #geom_point() + 
  #geom_pointrange(aes(ymin = low, ymax = high)) + 
  facet_wrap(~SubjectArea) + 
  ylab("Average Number of Authors") + 
  xlab("Publication Year") + 
  theme(legend.position = "none")
```

We will use the 95% confidence interval to make all claims of predictors or effects different zero. The confidence interval that does not include zero would be considered different from zero (to four decimal places). We make no directional predictions.

@@

```{r}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary"), 
       aes(Year, avg_career, color = sd_career)) +
  theme_classic() + 
  geom_point() +
  facet_wrap(~SubjectArea) + 
  theme(legend.position = "non") + 
  ylab("Average Career Length") +
  xlab("Year of Publication")
```

-  To analyze trends over time, we will calculate the average career length for each publication (i.e., average the author career length to create one score for each paper) and run a regression analysis using career length to predict year of publication. In order to show variance between individuals, we calculate the standard deviation of career length for each publication and run a regression analysis using this variance representation to predict publication year. These two variables will be used together. 
- Negative slopes would indicate more young scholars in later years (i.e., lower average career length as time increases). Positive slopes would indicate older scholars in later years (i.e., higher average career length as time increases). 
- Negative slopes imply that variability decreases over the years, so the average career length is more homogeneous. Positive slopes imply that variability increases over the years, so the average career length is varied across individuals (lots of different types of scholars). 
-   These analyses will be completed separately for each of the four large subject areas.

```{r}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
sample_size <- 13000

graph_data <- data.frame(
  "label" = label,
  "estimate" = avg_b_values,
  "type" = "M Coefficient",
  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
    bind_rows(
    data.frame(
    "label" = label,
    "estimate" = sd_b_values,
    "type" = "SD Coefficient",
    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
    ) %>% 
  bind_rows(
    data.frame(  
      "label" = label, 
      "estimate" = r2_values,
      "type" = "Effect Size",
      "low" = r2_low,
      "high" = r2_high)
  )

@@

```{r}
affs <- 35114
```

The total number of unique affiliation across all papers was `r affs`.

```{r}
ggplot(DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
       aes(Decade, `count(affiliation_ids)`)) + 
  #geom_point() + 
  geom_violin() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  ylab("Number of Affiliations") + 
  xlab("Decade")
```

@@

```{r}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
)

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "none")

# can probably figure out how to combine these feasibly to make it readable
# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
```

# can probably figure out how to combine these feasibly to make it readable

# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.

@@

- We will report descriptive statistics on the total number of publications and h-index for individuals overall.
  - Do this for each unique person and report averages
  - Do this for each publication and create an average for each publication

```{r}
avg_pub_count_author	<- apa_num(4.451816)
std_pub_count_author <- apa_num(6.901369)

avg_pub_count_paper <- apa_num(7.581413)
sd_pub_count_paper <- apa_num(5.797233)
avg_SD_pub_count_paper <- apa_num(7.140015)
SD_SD_pub_count_paper <- apa_num(5.10383)

avg_HIndex <- apa_num(14.242142)
std_HIndex <- apa_num(43.798203)
med_HIndex <- apa_num(2.0)

avg_of_avg_HIndex <- apa_num(28.136255)
std_of_avg_HIndex <- apa_num(38.013819)
avg_of_std_HIndex <- apa_num(36.430509)
std_of_std_HIndex <- apa_num(46.474619)
med_of_med_HIndex <- apa_num(5.0)
```

The average number of publications by authors on big team sciences papers is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The publication counts were averaged across authors for each publication, and then these average publication counts were averaged across publications *M* = `r avg_pub_count_paper` (*SD* = `r sd_pub_count_paper`). The average variability (i.e., the average standard deviation with authors of a manuscript) with publication counts of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ = `r SD_SD_pub_count_paper`).

The same process was completed with *h*-index for each author and publication. The average *h*-index for authors overall was *M* = `r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD* = `r std_of_avg_HIndex`), and the variability of *h*-index across manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ = `r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).

- Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
- A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
- We will separate these by each of the four subject areas.

```{r}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
sample_size <- 13000

graph_data <- data.frame(
  "label" = label,
  "estimate" = avg_b_values,
  "type" = "M Coefficient",
  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
    bind_rows(
    data.frame(
    "label" = label,
    "estimate" = sd_b_values,
    "type" = "SD Coefficient",
    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
    ) %>% 
  bind_rows(
    data.frame(  
      "label" = label, 
      "estimate" = r2_values,
      "type" = "Effect Size",
      "low" = r2_low,
      "high" = r2_high)
  )

@@

-   Last, we will examine the differences in representation for
    corresponding author sets versus all other authors. For papers with
    10 to 49 authors, we will use the three first authors and the last
    author to compare against other authors. For 50 to 99 authors, five
    first authors plus last will be used, and for all papers with more
    than 100 authors, we will use ten first authors and the last author.
    We will calculate the frequencies of each of the UN Sub-Regions for
    first authors versus other authors, converting these values to
    proportions. Given the expected small sample sizes of these
    contingency tables, we will group together titles based on the year
    of publication (assuming at least 5 publications per year, these may
    be binned by 5-year or smaller increments to increase sample size).
    For each grouping, we will calculate the effect size of the
    differences in frequencies comparing first authors to all other
    authors. Since this data is categorical, we will use Cramer's *V* to
    represent the effect size. If the effect size includes zero in its
    confidence interval, this result will imply that first and all other
    authors represent the same pattern of UN Sub-Region diversity. Any
    confidence interval that does include zero represents a difference
    in diversity.

```{r small-effects, warning = FALSE}
DF$small_first_gp <- DF$small_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r medium-effects, warning = FALSE}
DF$medium_first_gp <- DF$medium_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r large-effects, warning = FALSE}
DF$large_first_gp <- DF$large_first_gp %>% 
  filter(aff_un != "other") %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

@@

```{r author-gpe-figure, include = TRUE}
small_author + #theme(legend.position = "none") + 
medium_author + #theme(legend.position = "none") + 
large_author + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

ggsave("figure/author_country.png", width = 10, height = 7, 
       units = "in")
```

```{r effect-gpe-figure, include = TRUE}
small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")
